Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-20 arxiv_full_version/proof_gaussian_case.tex
arxiv version

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.

\begin{theorem}\label{thm_main_RMT_app}
	Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$.
	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any unit vector $w\in S$:
			\begin{align}\label{lem_cov_derv_eq}
				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
			\end{align}
				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
			\begin{align}\label{eq_a34extra}
				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{align}
\end{theorem}
%For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}

\paragraph{Proof Overview (cont'd).}
We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
%Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.
We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
}$$

To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
	\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
%}\HZ{what does this trick mean? use less technical words},
%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
%We define the $(n+N)\times (n+N)$ block matrix
 \begin{equation}\label{linearize_block}
    H \define \left( {\begin{array}{*{20}c}
   0 & \AF  \\
   \AF^{\top} & 0
%   {Z^{(2)}V} & 0 & 0
   \end{array}} \right).
 \end{equation}
For this block matrix, we define its resolvent as
$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
%as the resolvent of $H$,
for any complex value $z\in \mathbb C$.
Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
	\begin{equation} \label{green2}
	  G(z) =  \left( {\begin{array}{*{20}c}
			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
  \end{equation}

\paragraph{Variance asymptotic limit.}
In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
\be \label{defn_piw}
	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
\be\label{selfomega_a}
\begin{split}
	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %\label{selfomega_a000} \\
	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
\end{split}
\ee
The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
%\be\label{ratios}
% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
%\ee
Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} when $z=0$.
Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, % the trace of $$ converges to
\begin{align*}
  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
  \end{align*}
%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$. Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$. Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
%\begin{align}
%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
%\end{align}
where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.

\paragraph{Bias asymptotic limit.}
 For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %$W$
\begin{align}\label{calculate G'}
	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
\end{align}
Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
\begin{align}\label{cal G'0}
	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
\end{align}
To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
%\begin{align*}
%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
%\end{align*}
Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
%then taking implicit differentiation of equation \eqref{selfomega_a}
One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
%\begin{align}
%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
%\end{align}
%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.

As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.

%\paragraph{Schur complement and self-consistent equations.}
%
%First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
%By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
%Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
%We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
%On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
%Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
%We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
%A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.

\paragraph{How to derive the matrix limit?}
We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}V$ also follow an isotropic Gaussian distribution.
Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p\times p} } & (n_1+n_2)^{-1/2}\Lambda (Z^{(1)})^\top & (n_1+n_2)^{-1/2} (Z^{(2)})^\top  \\
   {(n_1+n_2)^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
   {(n_1+n_2)^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
%	\be\label{labelZ}
% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
We will study the following partial traces of the resolve $G(z)$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
\end{split}
\ee
To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
\begin{definition}[Resolvent minors]\label{defn_Minor}
	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1 a_2}$ to denote $ X_{a_1 a_2}$ when $a_1$ and $a_2$ are both not equal to $i$, and $X^{(i)}_{a_1 a_2}=0$ when $a_1 = i$ or $a_2 = i$.
	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
	\begin{align*}
		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
		  { -z\id_{p\times p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
    \end{array}} \right)^{(i)}\right]^{-1}.
	\end{align*}
\end{definition}
As a remark, we define the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G^{(i)}(z)$ in equation \eqref{defm}.

>>>>

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
%We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.

%\begin{theorem}\label{thm_main_RMT_app}
%
%	In the setting of Theorem \ref{thm_main_RMT},
%\end{theorem}
%For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}

%\paragraph{Proof Overview (cont'd).}
%We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
%Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
%Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.

We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}V$ also follow an isotropic Gaussian distribution.
Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p\times p} } & (n_1+n_2)^{-1/2}\Lambda (Z^{(1)})^\top & (n_1+n_2)^{-1/2} (Z^{(2)})^\top  \\
   {(n_1+n_2)^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
   {(n_1+n_2)^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
%	\be\label{labelZ}
% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
We will study the following partial traces of the resolve $G(z)$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
\end{split}
\ee
To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
\begin{definition}[Resolvent minors]\label{defn_Minor}
	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1 a_2}$ to denote $ X_{a_1 a_2}$ when $a_1$ and $a_2$ are both not equal to $i$, and $X^{(i)}_{a_1 a_2}=0$ when $a_1 = i$ or $a_2 = i$.
	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
	\begin{align*}
		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
		  { -z\id_{p\times p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
    \end{array}} \right)^{(i)}\right]^{-1}.
	\end{align*}
\end{definition}
As a remark, we define the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G^{(i)}(z)$ in equation \eqref{defm}.
